Mallows, Black-box combinatorial optimization, limited budget, ???

### 2020-09-06 paper/main.tex
more writing

@@

CEGO: Manuel.

@@

We use the implementation of GECO provided by the
authors\footnote{\url{https://cran.r-project.org/package=CEGO}}. Following the
original paper~\citep{ZaeStoFriFisNauBar2014}, we use and the GA that optimizes
the surrogate models uses a population size of 20, crossover rate of 0.5,
mutation rate of 1, tournament selection of size 2 and probability of 0.9,
interchange mutation (i.e., exchanging two randomly selected elements of the
permutation) and cycle crossover for permutations. The budget of each run of
the GA is \textcolor{red}{$10^5$} evaluations using the
surrogate-model. Although it is never stated in the original paper, the
implementation of CEGO generates a set of initial solutions of size \minit by
means of a max-min-distance sequential design: new solutions are added to the
set sequentially by maximizing the minimum distance to solutions already in the
set. These initial solutions are then evaluated on the actual objective
function and the result is used to build the initial surrogate model.

Here we use $\minit=20$.

@@

We implemented UMM in Python. The parameter settings that we use are...

@@

Computing system details: MANUEL

@@

@@

>>>>

%% Revision documents
\usepackage[dvipsnames]{xcolor}
\usepackage[normalem]{ulem}
% FIXME: \sout is not very good. It cannot handle commands within its argument.
\newcommand{\SuggestEdit}[3][red]{\textcolor{#1}{\sout{#2}}\textcolor{#1}{#3}}
\let\svthefootnote\thefootnote
\newcommand\colorfootnote[2][black]{\def\thefootnote{\color{#1}\svthefootnote}%
  \footnote{\color{#1}#2}\def\thefootnote{\color{black}\svthefootnote}}
\newcommand\RevComment[3][red]{\protect\colorfootnote[#1]{{\textbf{[#2: #3]}}}}
% Command for edits, command for commenting and color
\newcommand\newrevisor[3]{%%
  \colorlet{#1}{#3}
  \expandafter\newcommand\csname#1\endcsname[2]{\SuggestEdit[#1]{##1}{##2}}%%
  \expandafter\newcommand\csname#2\endcsname[1]{\RevComment[#1]{#2}{##1}}%%
}
\newrevisor{manuel}{MANUEL}{Purple}

@@

\manuel{CEGO: Manuel.}{}

@@

We use the implementation of GECO provided by the
authors\footnote{\url{https://cran.r-project.org/package=CEGO}}. Following the authors of CEGO~\citep{ZaeStoFriFisNauBar2014,ZaeStoBar2014:ppsn}, we use and the GA that optimizes
the surrogate models uses a population size of 20, crossover rate of 0.5,
mutation rate of 1, tournament selection of size 2 and probability of 0.9,
interchange mutation (i.e., exchanging two randomly selected elements of the
permutation) and cycle crossover for permutations. The budget of each run of
the GA is \textcolor{red}{$10^4$} evaluations using the
surrogate-model. Although it is never stated in the original paper, the
implementation of CEGO generates a set of initial solutions of size \minit by
means of a max-min-distance sequential design: new solutions are added to the
set sequentially by maximizing the minimum distance to solutions already in the
set. These initial solutions are then evaluated on the actual objective
function and the result is used to build the initial surrogate model.  Here we
use $\minit=20$.\MANUEL{\citet{ZaeStoBar2014:ppsn} uses 10 so we may want to change this}

The CPU time required for a single run of CEGO using these settings is larger
than a week.  For simplicity, we use Kendall Tau distance~\citep{?} in all
experiments\MANUEL{\citet{ZaeStoBar2014:ppsn} claims this is called Swap
  distance, could you double-check?}. Nevertheless,
\citet{ZaeStoFriFisNauBar2014} points out that CEGO performs best on the QAP
when using Hamming distance. We plan to extend our analysis of uMM to other
distance measures and to the dynamic selection of distance
measures~\citep{ZaeStoBar2014:ppsn}.

@@

We implemented UMM in Python 3. The parameter settings that we use are...

@@

\manuel{Computing system details: MANUEL}{%
  All experiments were run on Intel Xeon E5-2640 CPUs at 2.50\,GHz, 64\,GB RAM
  running CentOS Linux release 7.4.1708 (Core).  }

@@

For the LOP, we generated synthetic instances of size $n=20$, $m=200$, $\phi\in\{0.5,0.7,0.9\}$\MANUEL{what is $m$?}

In the case of the QAP and PFSP, we consider the same instances as
\citet{ZaeStoFriFisNauBar2014,ZaeStoBar2014:ppsn}, i.e.,
\texttt{nug12},\texttt{nug30},\texttt{tho30} and \texttt{kra32} for the QAP,
with $n$ equal to the number in the instance name, and \texttt{reC05},
\texttt{reC13}, \texttt{reC19}, \texttt{reC31} for the PFSP, with
$n \in \{20, 20, 30, 50\}$, respectively.

@@

Open questions:
\begin{itemize}
\item How difficult is to extend uMM to other distance metrics?
\item Can we plot the posterior probability of the optimal solution?
\end{itemize}
